HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex

These translation systems were used to translate texts derived from both NHS
24\footnote{\url{http://www.nhs24.com/}} and
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
NHS~24 is a public body providing healthcare and health-service
related information in Scotland, Cochrane is an international NGO
which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' which is part of the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.

@@

There are however a number of other serious consequences on focussing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\\
\item[Nominal argument structures,] which are completely ignored under HMEANT, are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

>>>>

These translation systems were used to translate texts derived from both NHS
24\footnote{\url{http://www.nhs24.com/}} and
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
NHS~24 is a public body providing healthcare and health-service
related information in Scotland, Cochrane is an international NGO
which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' in the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.

@@

There are however a number of other serious consequences on focussing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\\
\item[Nominal argument structures,] which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}
